### 2016-08-30 RA-L/experiment.tex
Changed the covariance Results!
Added the new two robot positioning figures.

\begin{figure*}[!htb]
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{
\begin{overpic}[width =0.415\columnwidth]{twoR_1.pdf}\put(15,65){$t$  = 30 s}\end{overpic}\hspace{-.5em}
\begin{overpic}[width =\figwid]{twoR_2.jpg}\put(15,65){$t$  = 60 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR_3.jpg}\put(15,65){$t$  = 90 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR_4.jpg}\put(15,65){$t$  = 120 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR_5.jpg}\put(15,65){$t$  = 150 s}
\end{overpic}}
\vspace{-2em}
\caption{\label{fig:storyReal}{Two robot positioning of two kilobot robots.  The boundary walls have nearly infinite friction, so the blue robot is stopped by the wall from $t = 30$s until the commanded input is directed away form the wall at $t=120$s, while the orange robot in free-space is unhindered.}
%\vspace{-2em}
}
\end{figure*}

@@

\subsection{Hardware Experiment: Control of Covariance}
To demonstrate covariance control $n$=100 robots were placed on the workspace and manually steered with a single light source, using friction with the boundary walls to vary the covariance from  -5000 to 10,000 pixel$^2$.  The resulting covariance is plotted in Fig.~\ref{fig:covExperiment}, along with snapshots of the swarm.

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{experiment.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:covExperiment}
Hardware demonstration steering 100 kilobot robots to desired covariance. The goal covariance is shown in green, the actual covariance in red. Frames above the plot show output from machine vision system and an overlaid covariance ellipse.
\vspace{-1em}
}
\end{figure}

>>>>

\begin{figure*}[!htb]
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{
\begin{overpic}[width =\figwid]{twoR1.pdf}\put(12,70){$t$  = 0 s}\end{overpic}
\begin{overpic}[width =\figwid]{twoR2.pdf}\put(12,70){$t$  = 60 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR3.pdf}\put(12,70){$t$  = 150 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR4.pdf}\put(12,70){$t$  = 160 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR5.pdf}\put(12,70){$t$  = 210 s}
\end{overpic}}
\vspace{-3em}
\caption{\label{fig:storyReal}{Positioning of two kilobots where they should reach their same color circle. The boundary walls have nearly infinite friction, so the green robot is stopped by the wall from $t = 60$s until the commanded input is directed away form the wall at $t=150$s, while the pink robot in free-space is unhindered.}
%\vspace{-1em}
}
\end{figure*}

@@

\subsection{Hardware Experiment: Control of Covariance}
To demonstrate covariance control $n$=100 robots were placed on the workspace and manually steered with lights, using friction with the boundary walls to vary the covariance from  -4000 to 4000 cm$^2$.  The resulting covariance is plotted in Fig.~\ref{fig:covExperiment}, along with snapshots of the swarm.

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{newExperiment.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:covExperiment}
Hardware demonstration steering 100 kilobot robots to desired covariance. The goal covariance is negative in first 100 seconds and is positive in the second 100 seconds. The actual covariance is shown in different trials. Frames above the plot show output from machine vision system and an overlaid covariance ellipse.
\vspace{-1em}
}
\end{figure}
